Internal Gravity Wave Breaking in White Dwarf Binaries

### 2019-08-01 writeups/paper.tex

    \documentclass[
        fleqn,
        usenatbib,
    ]{mnras}
    \usepackage{
        amsmath,
        amssymb,
        newtxtext,
        newtxmath,
        ae, aecompl,
        graphicx,
        booktabs,
    }
    \usepackage[T1]{fontenc}
    \usepackage[
        labelfont=bf, % caption names are labeled in bold
        font=scriptsize % smaller font for captions
    ]{caption}

@@

A full video of our higher-resolution run at $N_x = 768, N_z = 3072,
\mathrm{Re} = 1024$ is available
online\footnote{http://www.princeton.edu/~lecoanet/data/breaking\_wave.mov}. We
take this to be our fiducial simulation for the remainder of this paper, though
other simulations show qualitatively identical behavior. Slices of
$\overline{U}, \hat{F}$ across $z$ at various times $t$ are shown in
\autoref{fig:nl_fluxes}. While the behavior of $\overline{U}$ seems to conform
qualitatively with the predictions of \autoref{ss:crit_layer}, the behavior of
$\hat{F}$ exhibits two salient features: (i) the incident flux seems to
fluctuate greatly with time, and (ii) there seems to be a small transmitted
feature at many of the later times. We will discuss further these features in
\autoref{ss:reflectivity}, after first analyzing the propagation of the critical
layer.
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{plots/nl_fluxes.png}
    \caption{Plot of $\overline{U}(z, t)$ and $\hat{F}(z, t)$ respectively at
    various times over $z$ in our $\mathrm{Re} = 1024$ simulation.
    $\overline{U}, \hat{F}$ follow their definitions in \autoref{eq:mean_flow}
    and \autoref{eq:sbm_def}. $\overline{U}$ is given in units of $c_{ph, x} =
    \frac{\omega}{k_{x}}$ the critical layer flow velocity (see
    \autoref{ss:crit_layer}). The propagation of the critical layer towards
    lower $z$ and sharp deposition of $F$ at the critical layer are
    evident.}\label{fig:nl_fluxes}
\end{figure}

@@

\subsection{Kelvin-Helmholtz Instability and Critical Layer Width}

>>>>

    \documentclass[
        fleqn,
        usenatbib,
    ]{mnras}
    \usepackage{
        amsmath,
        amssymb,
        newtxtext,
        newtxmath,
        ae, aecompl,
        graphicx,
        booktabs,
    }
    \usepackage[T1]{fontenc}
    \usepackage[
        labelfont=bf, % caption names are labeled in bold
        font=scriptsize % smaller font for captions
    ]{caption}
    \usepackage[caption=false]{subfig} % subfigures

@@

A full video of our higher-resolution run at $N_x = 768, N_z = 3072,
\mathrm{Re} = 1024$ is available
online\footnote{http://www.princeton.edu/~lecoanet/data/breaking\_wave.mov}. We
take this to be our fiducial simulation for the remainder of this paper, though
other simulations show qualitatively identical behavior. Snapshots of the
velocity field $\bm{u}$ at select times can be found in \autoref{fig:snapshots}.
% convert yubo_000054.png -crop 2000x2000+150+250 out.png
\begin{figure*}
    \subfloat[$t=413.4$ At early times, the flow resembles a linear IGW lower in
    the simulation domain but breaks down into smaller-scale features at higher
    $z$. Some characteristic swirling motion can be seen in both $u_x, u_z$,
    highly suggestive of Kelvin-Helmholtz instabilities.]{
    \includegraphics[width=0.45\textwidth]{plots/yubo_000054.png}}\hfil
    %
    \subfloat[$t=658.5$ At a slightly later time, the mean flow in $u_x$ has
    become much more prominent and the critical layer $z_c$ has become much more
    definite. Small-scale fluctuations are still present in $u_z$ albeit at
    smaller amplitudes due to being in a denser region of the fluid.]{
    \includegraphics[width=0.45\textwidth]{plots/yubo_000086.png}}

    \subfloat[$t=1171.4$ The critical layer transition is now extremely sharp,
    and small swirls of limited vertical extent at the location of the critical
    layer in $u_z$ suggest that the Kelvin-Helmholtz instability is responsible
    for regulating the minimum width of this transition, a hypothesis explored
    in \autoref{ss:khi}.]{
    \includegraphics[width=0.45\textwidth]{plots/yubo_000153.png}}\hfil
    %
    \subfloat[$t=3437.8$ The end of the simulation shows very few significant
    qualitative differences from the previous snapshot, suggesting that the
    latter half of our simulation is temporally converged.]{
    \includegraphics[width=0.45\textwidth]{plots/yubo_000451.png}}

    \caption{Snapshots of $u_x, u_z$ in the fiducial simulation illustrating
    distinct phases of the evolution of the flow. Note that $\bar{U}_c \approx
    0.16$ for the parameters used.}\label{fig:snapshots}
\end{figure*}

Slices of
$\overline{U}, \hat{F}$ across $z$ at various times $t$ are shown in
\autoref{fig:nl_fluxes}. While the behavior of $\overline{U}$ seems to conform
qualitatively with the predictions of \autoref{ss:crit_layer}, the behavior of
$\hat{F}$ exhibits two salient features: (i) the incident flux seems to
fluctuate greatly with time, and (ii) there seems to be a small transmitted
feature at many of the later times. We will discuss further these features in
\autoref{ss:reflectivity}, after first analyzing the propagation of the critical
layer.
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{plots/nl_fluxes.png}
    \caption{Plot of $\overline{U}(z, t)$ and $\hat{F}(z, t)$ respectively at
    various times over $z$ in our $\mathrm{Re} = 1024$ simulation.
    $\overline{U}, \hat{F}$ follow their definitions in \autoref{eq:mean_flow}
    and \autoref{eq:sbm_def}. $\overline{U}$ is given in units of $c_{ph, x} =
    \frac{\omega}{k_{x}}$ the critical layer flow velocity (see
    \autoref{ss:crit_layer}). The propagation of the critical layer towards
    lower $z$ and sharp deposition of $F$ at the critical layer are
    evident.}\label{fig:nl_fluxes}
\end{figure}

@@

\subsection{Kelvin-Helmholtz Instability and Critical Layer Width}\label{ss:khi}
